### 2019-02-23 soc.tex
update includes formatting

\documentclass[a4paper, 12pt]{article}
\usepackage[top=2.5cm, left=3.5cm, right=1.5cm, bottom=2.5cm, includefoot]{geometry}

@@

% TOC AND LOF %
%-===========-%
\usepackage[subfigure,titles]{tocloft}          % for controlling LOF and LOF
\setlength{\cftfigindent}{0pt}                  % remove left LOF margin

\usepackage[nottoc]{tocbibind}                  % no TOC in TOC

@@

\setlength{\cftfigindent}{0pt}                  % lof indentation
\setlength{\cfttabindent}{0pt}                  % lot indentation

@@

\renewcommand*{\finentrypunct}{}                % don't end the reference with .

\renewcommand{\multinamedelim}{\addcomma\space} % use comma as delimeter
\renewcommand{\finalnamedelim}{\addspace a \space} % use a as final name delim
\renewbibmacro{in:}{}                           % don't use In:

\DeclareFieldFormat{labelnumberwidth}{[#1]}     % wrap references in square br.

% TABLES          %
% requires: float %
%-===============-%
\floatstyle{plaintop}
\restylefloat{table}
\usepackage{booktabs}                           % table formatting

% MISCELLANEOUS %
%-=============-%
\usepackage{amsmath, amstext}                   % math
\usepackage[font=small, labelfont=bf, figurename=Obr., tablename=Tab.]{caption}
\usepackage{enumitem}                           % lists

@@

\setmainfont{CMU Serif}                         % select font that suports bx sc

% ACRONYMS %
%-================-%
\usepackage[acronym,nopostdot,numberedsection,nogroupskip,nonumberlist]{glossaries}
\renewcommand{\acrfullformat}[2]{#2\space(#1)}  % switch long (short) for short (long)

@@

@@

% titles have sizes 18pt, 16pt and 14pt, respectively
% the space between the number and the text of the title is 1em = 10pt
\titleformat{\section}{\bfseries\scshape\fontsize{18pt}{21.6}\selectfont}{\thesection}{1em}{}
\titleformat{\subsection}{\bfseries\fontsize{16pt}{19.2}\selectfont}{\thesubsection}{1em}{}
\titleformat{\subsubsection}{\bfseries\fontsize{14pt}{16.8}\selectfont}{\thesubsubsection}{1em}{}

@@

\pagenumbering{gobble}   % suppress page numbering until TOC page

@@

\begin{document}
  % should fix some lines going to the margins
  \sloppy

@@

  % start page numbering at the first TOC page
  \newcounter{savepage}
  \setcounter{savepage}{\value{page}}%
  \pagenumbering{arabic}
  \setcounter{page}{\numexpr\value{savepage}-1}%

  % genereate TOC
  \tableofcontents

@@

  % create list of acronyms
  \glsaddall
  \glssetwidest{WYSIWYGGG}
  \setglossarystyle{alttree}
  \renewcommand{\glossarypreamble}{\vspace*{-2\baselineskip}}

  \printglossary[type=\acronymtype,title=Seznam zkratek]

@@

  % create the bibliography
  \renewcommand{\refname}{Použitá literatura}
  \printbibliography[heading=bibnumbered]

>>>>

\documentclass[a4paper, 12pt]{article}
\usepackage[top=2.5cm,
            left=3.5cm,
            right=1.5cm,
            bottom=2.5cm,
            includefoot]{geometry}              % set margins

@@

% TOC AND LOF %
%-===========-%
\usepackage[subfigure, titles]{tocloft}         % controlling lof and lot
\setlength{\cftfigindent}{0pt}                  % remove left lof margin

\usepackage[nottoc]{tocbibind}                  % no toc in toc

@@

\setlength{\cftfigindent}{0pt}                  % no lof indentation
\setlength{\cfttabindent}{0pt}                  % no lot indentation

@@

\renewcommand*{\finentrypunct}{}                % don't end the reference with .
\renewcommand{\multinamedelim}{\addcomma\space} % use comma as delimeter
\renewcommand{\finalnamedelim}{\addspace a \space} % use a as final name delim
\renewbibmacro{in:}{}                           % don't use In:

\DeclareFieldFormat{labelnumberwidth}{[#1]}     % wrap refs in square brackets

% TABLES          %
% requires: float %
%-===============-%
\floatstyle{plaintop}                           % table caption on top
\restylefloat{table}                            % -||-
\usepackage{booktabs}                           % table formatting

% MISCELLANEOUS %
%-=============-%
\usepackage{amsmath, amstext}                   % math

\usepackage[font=small,
            labelfont=bf,
            figurename=Obr.,
            tablename=Tab.]{caption}            % captions

\usepackage{enumitem}                           % lists

@@

\setmainfont{CMU Serif}                         % a font that suports bx sc

% ACRONYMS %
%-========-%
\usepackage[acronym,                            % use acronyms
            nopostdot,                          % no dot at end of 2nd column
            numberedsection,                    % number glossary
            nogroupskip,                        % no grouping by same letter
            nonumberlist]{glossaries}           % no page numbers

\renewcommand{\acrfullformat}[2]{#2\space(#1)}  % long (short) to short (long)

\setglossarystyle{alttree}                      % set style of glossary

\renewcommand{\glossarypreamble}{\vspace*{-2\baselineskip}} % reduce glossaries title spacing

@@

\glsaddall                                      % add all acronyms
\glsfindwidesttoplevelname

@@

% titles have sizes 18pt, 16pt and 14pt, respectively
% the space between the number and the text of the title is 1em
\titleformat{\section}{\bfseries\scshape\fontsize{18pt}{21.6}\selectfont}{\thesection}{1em}{}
\titleformat{\subsection}{\bfseries\fontsize{16pt}{19.2}\selectfont}{\thesubsection}{1em}{}
\titleformat{\subsubsection}{\bfseries\fontsize{14pt}{16.8}\selectfont}{\thesubsubsection}{1em}{}

@@

\pagenumbering{gobble}                          % suppress page numbering

@@

\begin{document}
  % fixes some lines going to the margins
  \sloppy

@@

  % resume page numbering
  \newcounter{savepage}
  \setcounter{savepage}{\value{page}}%
  \pagenumbering{arabic}
  \setcounter{page}{\numexpr\value{savepage}-1}%

  % genereate toc
  \tableofcontents

@@

  % create list of acronyms
  \printglossary[type=\acronymtype, title=Seznam zkratek]

@@

  % create the bibliography
  \printbibliography[heading=bibnumbered, title=Použitá literatura]
